---
title: "SF-Math analysis"
author: "Rose Schneider"
date: "5/13/2018"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
require("knitr")
opts_knit$set(root.dir = "~/Documents/Projects/sf_math/") #this is specific to RMS, change accordingly
library(tidyverse)
library(magrittr)
library(langcog)
```

#Setup

##Loading data
Each task is stored as a separate CSV. Need to tidy and check each sheet individually.
```{r}
#First load Give N
given.raw <- read.csv("Data/GiveN.csv")

#Then load Highest Count
highestcount.raw <- read.csv("Data/HighestCount.csv")

#Then load SF
sf.raw <- read.csv("Data/SF.csv")

#Then load Next Number
nextnumber.raw <- read.csv("Data/NextNumber.csv")

#Then load Math Facts
mathfacts.raw <- read.csv("Data/MathFacts.csv")

#Then load Indefinite
indefinite.raw <- read.csv("Data/Indefinite.csv")

#combine for looping
tasks <- list(given.raw, highestcount.raw, sf.raw, 
              nextnumber.raw, mathfacts.raw, indefinite.raw)
```

##Tidy data
Remove all exclusions. Make sure that anyone who is excluded by Give N is not included in other analyses.
```{r}
#make a df of total exclusions across all tasks
check_exclusions <- function(df){
    exclusions <- df %>%
      filter(exclude == 1)%>%
      distinct(SID, age, sex, experimenter, location, exclude, exclude_reason)
    
    exclusions$task = deparse(substitute(df))
    if (length(exclusions$SID) > 0) {
    return(exclusions)
    } else {
      return("No exclusions")
    }
}

#check each task
given.exclusions <- check_exclusions(given.raw)
highestcount.exclusions <- check_exclusions(highestcount.raw)
sf.exclusions <- check_exclusions(sf.raw)
nextnumber.exclusions <- check_exclusions(nextnumber.raw)
mathfacts.exclusions <- check_exclusions(mathfacts.raw)
indefinite.exclusions <- check_exclusions(indefinite.raw) #deal with this later

#bind these together
all_exclusions <- bind_rows(given.exclusions, highestcount.exclusions, 
                            sf.exclusions, nextnumber.exclusions, 
                            mathfacts.exclusions)

#review these guys manually
#NB RMS - you need to check on exclusion criteria

##once you have reviewed these guys manually, run the below code
exclusion_SIDs <- as.vector(all_exclusions$SID)

'%!in%' <- function(x,y)!('%in%'(x,y))

exclude <- function(df){
  df %<>%
    filter(SID %!in% exclusion_SIDs)
}

given.df <- exclude(given.raw)
highestcount.df <- exclude(highestcount.raw)
nextnumber.df <- exclude(nextnumber.raw)
sf.df <- exclude(sf.raw)
mathfacts.df <- exclude(mathfacts.raw)
```

##Sanity checks
###Do we have the same number (and same participants) for each task?
```{r}
#get unique IDs
get_unique_SID <- function(df){
  unique <- df %>%
    distinct(SID, age)
  
  unique$task = deparse(substitute(df))
  return(unique)
}

unique.given <- get_unique_SID(given.df)
unique.highestcount <- get_unique_SID(highestcount.df)
unique.sf <- get_unique_SID(sf.df)
unique.nextnumber <- get_unique_SID(nextnumber.df)
unique.mathfacts <- get_unique_SID(mathfacts.df)

#bind all unique IDs and ages together
all_unique <- bind_rows(unique.given, unique.highestcount, unique.sf, 
          unique.nextnumber, unique.mathfacts)%>%
  mutate(SID = factor(SID))

#dumb way to do this, but there need to be 5 tasks per participant
#find all participants that do not have 5 tasks
unique.check <- all_unique %>%
  group_by(SID, age)%>%
  summarise(n = n())%>%
  filter(n != 5)

##NB - you must manally review these. 
##To-do for RMS: You should automate whether these are included or excluded
```



##Coding check
Is everything marked as correct actually correct?

#Highest count
```{r}
#relation between initial and final
initial_final <- highestcount.df %>%
  distinct(SID, age, initial_highest, final_highest)%>%
  mutate(initial_highest = as.numeric(initial_highest), 
         initial_final = as.numeric(final_highest))

ggplot(initial_final, aes(x = initial_highest, y = final_highest, color = age)) +
  geom_point()

#distribution of initial
ggplot(initial_final, aes(x = initial_highest)) + 
  geom_histogram()

ggplot(initial_final, aes(x = final_highest)) + 
  geom_histogram()
```